On the surprising effectiveness of a simple matrix exponential derivative approximation, with application to global SARS-CoV-2

### 2023-09-14 manuscript/revision_letter.tex
more response

\begin{reply}
	We thank you for sharing these concerns.  Before responding, let us point out that we have now added a simulation section (similar to that which you specify below) to the manuscript.   Now, we would like to argue that the decisions we made in structuring our manuscript are well-motivated based on our work in two other papers.
	\begin{enumerate}
		\item First,
	\end{enumerate}
\end{reply}

@@

>>>>

\begin{reply}
	We thank you for sharing your concerns, which we take seriously.  Before responding, let us point out that we have now added a simulation section (similar to that which you specify below) to the manuscript.   Now, we would like to argue that the decisions we made in structuring our manuscript are well-motivated based on our other work.
	\begin{enumerate}
		\item First, we have written a companion paper \citet{magee2023random} (minor revisions at Systematic Biology), which presents the basic approach, implements a thorough simulation study and applies the methodology to 3 real-world data analyses of varying dimensions and differing fixed-effect structures.

		\item Second, when writing this paper, we had a clear understanding of the theoretical guarantees provided by surrogate-trajectory HMC.  Our paper \citet{glatt2020accept} (to appear at Annals of Applied Probability) proves that the surrogate-trajectory HMC transition kernel maintains detailed balance and that the algorithm samples from the target distribution with the same guarantees as vanilla HMC.  The results of \citet{glatt2020accept} hold for general state spaces, regardless of dimensionality.
	\end{enumerate}

Despite these theoretical guarantees, the method of \citet{magee2023random} performed even better than expected in terms of relatively high acceptance rates and relatively low autocorrelation between samples.  From our other previous work with surrogate-trajectory HMC \citep{li2019neural}, we knew this must suggest that the first-order matrix exponential gradient approximation must be pretty good.   
As a result, our goal in this paper was to find out what makes the first-order approximation so good and provide a salient example that illustrates the efficacy of the approximation in higher dimensions.

In short, our original goal was not to prove validity of the general methodology, which we saw as already established through simulation studies, real-world analyses and measure theoretic probability.

Again, we thank you for sharing your concerns and hope that the broader context of our work helps explain the positioning of our manuscript.  Probably more importantly, we have updated our manuscript with a thorough simulation study (see below).
\end{reply}

@@

\begin{reply}
Simulaiton. TBD.
\end{reply}
